Quickie for importing tasks to OmniFocus 3

### 2022-04-02 _posts/2022-04-02-quickie-for-importing-tasks-to-omnifocus-3/quickie-for-importing-tasks-to-omnifocus-3.Rmd
typos

One of the problems, I now realize, was the notion of *contexts* - each to-do item could be assigned to one, *and only one*, context, like "online" or "supermarket" or "home", describing the setting where a task could be done. The problem was that there were many tasks that could be done in multiple contexts, but no way to mark them as such. One user I talked with on one of the forums explained that the way to think about it was that I myself could be in multiple simultaneous contexts, like "home" and "online", and that tasks that matched either of those would appear. It sort of made sense, but it still never felt natural and I eventually dropped it again.

>>>>

One of the problems, I now realize, was the notion of *contexts* - each to-do list could be assigned one, *and only one*, context, like "online" or "supermarket" or "home", describing the setting where a task could be done. The problem was that there were many tasks that could be done in multiple contexts, but no way to mark them as such. One user I talked with on one of the forums explained that the way to think about it was that I myself could be in multiple simultaneous contexts, like "home" and "online", and that tasks that matched either of those would appear. It sort of made sense, but it still never felt natural and I eventually dropped it again.
